% !TEX TS-program = xelatex
%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{etaremune}
% \usepackage{fontawesome} % Removed to avoid missing FontAwesome tfm issues
% \input{glyphtounicode} % Optional for pdfLaTeX; XeLaTeX is Unicode-native
\usepackage{fontawesome5}
\usepackage{lastpage}
\usepackage{ifthen}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% Footer: show updated date on bottom-right only on last page
\newcommand{\UpdatedOn}{\number\year-\ifnum\month<10 0\fi\number\month-\ifnum\day<10 0\fi\number\day}
\setlength{\footskip}{12pt}
\fancyfoot[R]{\scriptsize \ifthenelse{\equal{\thepage}{\pageref{LastPage}}}{Updated: \UpdatedOn}{}}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine readable/ATS parsable (pdfLaTeX only)
\ifdefined\pdfgentounicode
  \pdfgentounicode=1
\fi

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{etaremune}}
\newcommand{\resumeItemListEnd}{\end{etaremune}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Hao Zeng}
    \vspace{0.5em}\\
    {\small Postdoc, Department of Statistics and Data Science, Southern University of Science and Technology}
    % \small "Heterogeneity nourishes statistics; independence begets probability; uncertainty is eternal."
\end{center}

\begin{center}
    \small \faIcon{envelope}\ \href{mailto:zenghao.acmail@gmail.com}{zenghao.acmail@gmail.com} $|$
    \faIcon{graduation-cap}\ \href{https://scholar.google.com/citations?user=-EiBHeIAAAAJ&hl=en}{Google Scholar} $|$
    \faIcon{home}\ \href{https://zenghao-stat.github.io}{Homepage: zenghao-stat.github.io}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Gregory and Paula Chow Institute for Studies in Economics, Xiamen University}{Sept. 2020 -- Jun. 2024}
      {Ph.D. in Statistics, Supervised by Wei Zhong, Xingbai Xu, and Tuo Liu}{}
    
    \resumeSubheading
      {Wang Yanan Institute for Studies in Economics, Xiamen University}{Sept. 2018 -- Jun. 2020}
      {M.S. in Quantitative Economics}{Transfer to Ph.D. in Statistics}
    
    \resumeSubheading
      {School of Mathematics, Shandong University}{Sept. 2014 -- Jun. 2018}
      {B.S. in Mathematics (Peng's Class: Base of Financial Mathematics \& Financial Engineering)}{}
  \resumeSubHeadingListEnd


%-----------RESEARCH INTERESTS-----------
\section{Research Area}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Statistical Machine Learning}{: Model Free Predictive Inference, Conformal Prediction, Transfer Learning} \\
     \textbf{Interdisciplinary Research}{: Large Language Models, Spatial Statistics, Econometrics, and Biostatistics}
    }}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Southern University of Science and Technology \& National University of Singapore}{Jul. 2024 -- Present}
      {Postdoctoral Researcher in Statistics, Supervised by Bingyi Jing, Hongxin Wei, and Wang Zhou}{}
    
    \resumeSubheading
      {Department of Statistics, National University of Singapore}{May 2023 -- Oct. 2023}
      {Visiting Researcher, Cooperated with Tao Yu}{}
    
    \resumeSubheading
      {School of Economics, Xiamen University}{Fall 2022}
      {Teaching Assistant in Probability Introduction (Undergraduate)}{}
    
    \resumeSubheading
      {School of Economics, Xiamen University}{Spring 2022}
      {Teaching Assistant in Real Analysis (Undergraduate)}{}
    \resumeSubheading
      {School of Economics, Xiamen University}{Fall 2021}
      {Teaching Assistant in Advanced Probability Theory (Postgraduate)}{}
    
    \resumeSubheading
      {School of Economics, Xiamen University}{Spring 2021}
      {Teaching Assistant in Real Analysis (Undergraduate)}{}
    
    \resumeSubheading
      {School of Economics, Xiamen University}{Fall 2019}
      {Teaching Assistant in Advanced Econometrics I (Postgraduate)}{}
  \resumeSubHeadingListEnd


%-----------PUBLICATIONS-----------
\section{Publications}
(* means corresponding author, $^\dagger$ means equal contribution, \(^\diamond\) means supervised students.)
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Journal Articles}}{}
\resumeItemListStart
  \resumeItem{\textbf{Hao Zeng}, Wei Zhong, \& Xingbai Xu (2025). ``Transfer Learning for Spatial Autoregressive Models with Application to U.S. Presidential Election Prediction.'' (Accepted for \textit{\textbf{Journal of Business \& Economic Statistics}}, econometrics and statistics top journal)} 
  \resumeItem{Kangdao Liu, Tianhao Sun, \textbf{Hao Zeng}, Yongshan Zhang, Chi-Man Pun, \& Chi-Man Vong (2025). ``Spatial-Aware Conformal Prediction for Trustworthy Hyperspectral Image Classification.'' \textit{\textbf{IEEE Transactions on Circuits and Systems for Video Technology}}. (CAS Q1 journal, Top)}
  \resumeItem{\textbf{Hao Zeng}, Chuang Wan, Wei Zhong, \& Tuo Liu (2024). ``Robust Integrative Analysis via Quantile Regression with Homogeneity and Sparsity.'' \textit{\textbf{Journal of Statistical Planning and Inference}}.}
  \resumeItem{Chuang Wan$^\dagger$, \textbf{Hao Zeng$^\dagger$*}, Wenyang Zhang$^\dagger$, Wei Zhong$^\dagger$, \& Changliang Zou$^\dagger$ (2024). ``Data‐driven Estimation for Multithreshold Accelerated Failure Time Model.'' \textit{\textbf{Scandinavian Journal of Statistics}}.}
  \resumeItem{Wenqian Chen, \textbf{Hao Zeng}, Xiaoya Wang, Qiuping Xu, Panpan Liu, Liwei Zhang, Yingyue Hou, Qing Luo, Xueye Liu, Zhe Jiang, Zhiyuan Zhou, Jiang Chen, \& Jing Guo (2022). ``A Structural Equation Modeling Approach to Determine the Correlation between the Vertical and Sagittal Skeletal Patterns and Posterior Basal Bones Mismatching in Patients with Skeletal Class III Malocclusion.'' \textit{\textbf{American Journal of Orthodontics and Dentofacial Orthopedics}}. (Cover paper)}
  \resumeItem{Wenqian Chen, \textbf{Hao Zeng}, Luna Sun, Qiuping Xu, Zhenxue Chen, Yunhan Sun, Qi Jia, Chengyun Liu, \& Jing Guo (2021). ``Match of the Bimaxillary Basal Bone Arches and Its Variations among Individuals.'' \textit{\textbf{Scanning}} 2021 (1): 9625893.}
\resumeItemListEnd

  \resumeProjectHeading{\textbf{Conference Papers}}{}
  \resumeItemListStart
    \resumeItem{\textbf{Hao Zeng$^\dagger$}, Kangdao Liu$^\dagger$, Bingyi Jing, \& Hongxin Wei (2025). ``Parametric Scaling Law of Tuning Bias in Conformal Prediction.'' \textit{\textbf{42nd International Conference on Machine Learning}}. (AI Top conference)}
    \resumeItem{Huajun Xi$^\diamond$, Kangdao Liu, \textbf{Hao Zeng}, Wenguang Sun, \& Hongxin Wei (2025). ``Exploring the Noise Robustness of Online Conformal Prediction.'' \textit{\textbf{39th Annual Conference on Neural Information Processing Systems}}. (AI Top conference)
    }
    \resumeItem{Kangdao Liu, \textbf{Hao Zeng}, Jianguo Huang, Huiping Zhuang, Chi-Man Vong, \& Hongxin Wei (2025). ``C-Adapter: Adapting Deep Classifiers for Efficient Conformal Prediction Sets.'' \textit{\textbf{28th European Conference on Artificial Intelligence}}.}
  \resumeItemListEnd
    
    \resumeProjectHeading
      {\textbf{Working Papers}}{}
      \resumeItemListStart
        \resumeItem{Jingyi Zhang$^\diamond$, Yang Yue, Wei Zhong, \& \textbf{Hao Zeng*} (2025). ``Robust Estimation of Grouped Network Vector Autoregression: An Empirical Analysis Based on China Air Quality Data.'' (Submitted to \textit{Statistical Research})}
        \resumeItem{Huipeng Huang$^\diamond$, Wenbo Liao, Huajun Xi, \textbf{Hao Zeng}, Mengchen Zhao, \& Hongxin Wei (2025). ``Selective Labeling with False Discovery Rate Control.'' (Submitted to ICLR 2026)}
        \resumeItem{Zhenlong Liu$^\diamond$, \textbf{Hao Zeng}, Weiran Huang, \& Hongxin Wei (2025). ``High-Power Training Data Identification with Provable Statistical Guarantees.'' (Submitted to ICLR 2026)}
        \resumeItem{\textbf{Hao Zeng}$^\dagger$, Jianguo Huang$^\dagger$\(^\diamond\), Bingyi Jing, Hongxin Wei, \& Bo An (2025). ``PAC Reasoning: Controlling the Performance Loss for Efficient Reasoning.'' (Submitted to ICLR 2026)}
        \resumeItem{Hongfu Gao, Feipeng Zhang, \textbf{Hao Zeng}, Deyu Meng, Bingyi Jing, \& Hongxin Wei (2025). ``Exploring Imbalanced Annotations for Effective In-Context Learning.'' (Submitted to ICLR 2026)}
        \resumeItem{Xuanning Zhou$^\diamond$, Zihao Shi$^\diamond$, \textbf{Hao Zeng}, Xiaobo Xia, Bingyi Jing, \& Hongxin Wei (2025). ``Semi-Supervised Conformal Prediction with Unlabeled Nonconformity Score.'' (Submitted to CVPR 2026)}
        \resumeItem{\textbf{Hao Zeng}, Bingyi Jing, \& Hongxin Wei (2025). ``Conditional Tuning in Conformal Prediction.''}
        \resumeItem{\textbf{Hao Zeng}, Bingyi Jing, \& Hongxin Wei (2025). ``The Double Descent of Conformal Prediction.''}
        \resumeItem{\textbf{Hao Zeng}, Kangdao Liu, Bingyi Jing, \& Hongxin Wei (2025). ``On Tuning Bias in Conformal Prediction.''}
        \resumeItem{\textbf{Hao Zeng}, \& Jianguo Huang$^\diamond$ (2025). ``PAC Accelerate: A Statistically Guaranteed Acceleration Method for Large Generative Models.''}
        \resumeItem{\textbf{Hao Zeng}, \& Jianguo Huang$^\diamond$ (2025). ``Group-Conditional PAC Reasoning: Groupwise Efficient Reasoning with Statistical Guarantees.''}
        \resumeItem{\textbf{Hao Zeng}, Jiajun Sun$^\diamond$, Bingyi Jing, \& Wei Zhong (2025). ``Test-time Valid Selection of Conformal Sets via Gaussian Stability.'' Working paper.}
        \resumeItem{\textbf{Hao Zeng}, Junxian Liu$^\diamond$, Bingyi Jing, \& Hongxin Wei (2025). ``Efficient Backward Conformal Prediction.'' Working paper.}
      \resumeItemListEnd
    
    \resumeProjectHeading
      {\textbf{Software}}{}
      \resumeItemListStart
        \resumeItem{Chuang Wan, \textbf{Hao Zeng}, Wei Zhong, \& Changliang Zou (2023). ``MTAFT: Data-Driven Estimation for Multi-Threshold Accelerate Failure Time Model.'' \href{https://cran.r-project.org/web/packages/MTAFT/index.html}{https://cran.r-project.org/web/packages/MTAFT/index.html}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd






\section{Conference Presentations}
\resumeSubHeadingListStart
    \resumeSubSubheading
        {Talk in \textbf{The 2021 Forum for Doctoral Students in Quantitative Economics}}{Dec. 2021, Xiamen}
    \resumeSubSubheading
        {Invited Talk in \textbf{Xiamen University 2021 Symposium on Modern Statistics}}{Dec. 2021, Xiamen}
    \resumeSubSubheading
        {Invited Talk in \textbf{2023 PhD Forum on Econometric Modeling and Economic Policy Research}}{Nov. 2023, Beijing}
    \resumeSubSubheading
        {Poster in \textbf{Conference of the Youth Association of the Chinese Association for Industrial Statistics}}{Mar. 2024, Xuzhou}
    \resumeSubSubheading
        {Invited Talk in \textbf{The 1st Outstanding PhD Forum in Economics and Management Statistics}}{Jun. 2024, Xiamen}
    \resumeSubSubheading
        {Invited Talk in \textbf{The 2nd Joint Conference on Statistics and Data Science}}{Jul. 2024, Kunming}
    \resumeSubSubheading
        {Talk in \textbf{The 13th Conference on Probability and Statistics}}{Nov. 2024, Xiamen}
    \resumeSubSubheading
        {Poster in \textbf{The 3rd Joint Conference on Statistics and Data Science}}{Jul. 2025, Hangzhou}
    \resumeSubSubheading
        {Poster in \textbf{Forty-Second International Conference on Machine Learning}}{Jul. 2025, Vancouver, Canada}
\resumeSubHeadingListEnd


\section{Academic Services}
\begin{itemize}[leftmargin=0.15in, label={}]
   \item \textbf{Journal Reviewer} 
 {International Statistical Review}, {Journal of Multivariate Analysis}, {Spatial Economic Analysis}, and {Quarterly Journal of Economics and Management}.\\
  \item \textbf{Conference Reviewer} 
 {International Conference on Artificial Intelligence and Statistics (AISTATS), AAAI Conference on Artificial Intelligence(AAAI), International Conference on Machine Learning (ICML), International Conference on Learning Representations (ICLR), IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR)}
\end{itemize}



  \section{Awards}
  \resumeSubHeadingListStart
    \resumeSubSubheading
      {Excellent Teaching Assistant in Fall 2022-2023, Xiamen University}{2024}
    \resumeSubSubheading
      {Meritorious Winner, Interdisciplinary Contest in Modeling, USA}{2016}
    \resumeSubSubheading
      {3rd Prize at the Provincial Level, Mathematics Competition for Chinese College Students}{2016}
    \resumeSubSubheading
      {2nd Prize at the Provincial Level, China Undergraduate Mathematical Contest in Modeling}{2015}
    \resumeSubSubheading
      {1st Prize for Outstanding Students, Shandong University}{2015}
    \resumeSubSubheading
      {Merit Student, Shandong University}{2015} % 三好学生
  \resumeSubHeadingListEnd

\end{document}
