% !TEX TS-program = pdflatex
\documentclass[10pt]{article}
\usepackage[english]{babel}
\usepackage[hidelinks]{hyperref}
\usepackage{geometry}
\usepackage{etaremune}
% \geometry{margin=1in}

\begin{document}
\centerline{\Large{\textbf{Publications and Working Papers}}}
\vspace{10pt}
\centerline{(* means corresponding author, $^\dagger$ means equal contribution, \(^\diamond\) means supervised students)}

\section*{Journal articles}
\begin{etaremune}
\item \underline{Hao Zeng}, Wei Zhong, and Xingbai Xu (2025). ``Transfer Learning for Spatial Autoregressive Models with Application to U.S. Presidential Election Prediction.'' \textit{Journal of Business \& Economic Statistics}. (Accepted, econometrics and statistics top journal, ABS 4\(\star\))
\item Kangdao Liu, Tianhao Sun, \underline{Hao Zeng}, Yongshan Zhang, Chi-Man Pun, and Chi-Man Vong (2025). ``Spatial-Aware Conformal Prediction for Trustworthy Hyperspectral Image Classification.'' \textit{IEEE Transactions on Circuits and Systems for Video Technology} 35 (9): 8754–8766. (CAS Q1 journal, Top)
\item \underline{Hao Zeng}, Chuang Wan, Wei Zhong, and Tuo Liu (2024). ``Robust Integrative Analysis via Quantile Regression with Homogeneity and Sparsity.'' \textit{Journal of Statistical Planning and Inference} 234 (January): 106196.
\item Chuang Wan$^\dagger$, \underline{Hao Zeng$^\dagger$*}, Wenyang Zhang$^\dagger$, Wei Zhong$^\dagger$, and Changliang Zou$^\dagger$ (2024). ``Data‐driven Estimation for Multithreshold Accelerated Failure Time Model.'' \textit{Scandinavian Journal of Statistics} 52 (1): 447–468.
\item Wenqian Chen, \underline{Hao Zeng}, Xiaoya Wang, Qiuping Xu, Panpan Liu, Liwei Zhang, Yingyue Hou, Qing Luo, Xueye Liu, Zhe Jiang, Zhiyuan Zhou, Jiang Chen, and Jing Guo (2022). ``A Structural Equation Modeling Approach to Determine the Correlation between the Vertical and Sagittal Skeletal Patterns and Posterior Basal Bones Mismatching in Patients with Skeletal Class III Malocclusion.'' \textit{American Journal of Orthodontics and Dentofacial Orthopedics} 162 (6): e277–294. (Cover paper)
\item Wenqian Chen, \underline{Hao Zeng}, Luna Sun, Qiuping Xu, Zhenxue Chen, Yunhan Sun, Qi Jia, Chengyun Liu, and Jing Guo (2021). ``Match of the Bimaxillary Basal Bone Arches and Its Variations among Individuals.'' \textit{Scanning} 2021 (1): 9625893.
\end{etaremune}

\section*{Conference papers}
\begin{etaremune}
\item \underline{Hao Zeng$^\dagger$}, Kangdao Liu$^\dagger$, Bingyi Jing, and Hongxin Wei (2025). ``Parametric Scaling Law of Tuning Bias in Conformal Prediction.'' \textit{42nd International Conference on Machine Learning (ICML 2025)}. (AI/ML Top)
\item Huajun Xi$^\diamond$, Kangdao Liu, \underline{Hao Zeng}, Wenguang Sun, and Hongxin Wei (2025). ``Exploring the Noise Robustness of Online Conformal Prediction.'' \textit{39th Annual Conference on Neural Information Processing Systems (NeurIPS 2025)}. (AI/ML Top)
\item Kangdao Liu, \underline{Hao Zeng}, Jianguo Huang, Huiping Zhuang, Chi-Man Vong, and Hongxin Wei (2025). ``C-Adapter: Adapting Deep Classifiers for Efficient Conformal Prediction Sets.'' \textit{28th European Conference on Artificial Intelligence}.
\end{etaremune}

\section*{Working papers}
\begin{etaremune}
\item Jingyi Zhang$^\diamond$, Yang Yue, Wei Zhong, and \underline{Hao Zeng*} (2025). ``Robust Estimation of Grouped Network Vector Autoregression: An Empirical Analysis Based on China Air Quality Data.'' (Submitted to \textit{Statistical Research})
\item Huipeng Huang$^\diamond$, Wenbo Liao, Huajun Xi, \underline{Hao Zeng}, Mengchen Zhao, and Hongxin Wei (2025). ``Selective Labeling with False Discovery Rate Control.'' (Submitted to \textit{The 14th International Conference on Learning Representations (ICLR 2026)})
\item Zhenlong Liu$^\diamond$, \underline{Hao Zeng}, Weiran Huang, and Hongxin Wei (2025). ``High-Power Training Data Identification with Provable Statistical Guarantees.'' (Submitted to \textit{The 14th International Conference on Learning Representations (ICLR 2026)})
\item \underline{Hao Zeng}$^\dagger$, Jianguo Huang$^\dagger$\(^\diamond\), Bingyi Jing, Hongxin Wei, and Bo An (2025). ``PAC Reasoning: Controlling the Performance Loss for Efficient Reasoning.'' (Submitted to \textit{The 14th International Conference on Learning Representations (ICLR 2026)})
\item Hongfu Gao, Feipeng Zhang, \underline{Hao Zeng}, Deyu Meng, Bingyi Jing, and Hongxin Wei (2025). ``Exploring Imbalanced Annotations for Effective In-Context Learning.'' (Submitted to \textit{The 14th International Conference on Learning Representations (ICLR 2026)})
\item Xuanning Zhou$^\diamond$, Zihao Shi$^\diamond$, \underline{Hao Zeng}, Xiaobo Xia, Bingyi Jing, and Hongxin Wei (2025). ``Semi-Supervised Conformal Prediction with Unlabeled Nonconformity Score.'' (Submitted to \textit{The IEEE/CVF Conference on Computer Vision and Pattern Recognition 2026 (CVPR 2026)})
\item \underline{Hao Zeng}, Bingyi Jing, and Hongxin Wei (2025). ``Conditional Tuning in Conformal Prediction.''
\item \underline{Hao Zeng}, Bingyi Jing, and Hongxin Wei (2025). ``The Double Descent of Conformal Prediction.''
\item \underline{Hao Zeng}, Kangdao Liu, Bingyi Jing, and Hongxin Wei (2025). ``On Tuning Bias in Conformal Prediction.''
\item \underline{Hao Zeng}, and Jianguo Huang$^\diamond$ (2025). ``PAC Accelerate: A Statistically Guaranteed Acceleration Method for Large Generative Models.''
\item \underline{Hao Zeng}, and Jianguo Huang$^\diamond$ (2025). ``Group-Conditional PAC Reasoning: Groupwise Efficient Reasoning with Statistical Guarantees.''
\item \underline{Hao Zeng} (2025). ``A Note on the Impossibility of Conditional PAC-Efficient Reasoning.''
\item \underline{Hao Zeng}, Jiajun Sun$^\diamond$, Bingyi Jing, and Wei Zhong (2025). ``Test-time Valid Selection of Conformal Sets via Gaussian Stability.''
\item \underline{Hao Zeng}, Junxian Liu$^\diamond$, Bingyi Jing, and Hongxin Wei (2025). ``Efficient Backward Conformal Prediction.''
\item \underline{Hao Zeng}, Wei Zhong, Chuang Wan (2025). ``Selective Inference for the Identified Groups in Network Vector Autoregressive Model.''
\item \underline{Hao Zeng}, Huipeng Huang$^\diamond$, Jianguo Huang$^\diamond$, Bingyi Jing, and Hongxin Wei (2025). ``HyPAC:\@ Cost-Efficient LLM--Human Hybrid Annotation with PAC Error Guarantees.''
\item Xiaoqi Qiu$^\dagger$ $^\diamond$, \underline{Hao Zeng}$^\dagger$, Bingyi Jing, and Hongxin Wei (2025). ``LLM Provenance Testing via Constrained Model Confidence Sets.''
\end{etaremune}

\section*{Software}
\begin{etaremune}
\item Chuang Wan, \underline{Hao Zeng}, Wei Zhong, and Changliang Zou (2023). ``MTAFT: Data-Driven Estimation for Multi-Threshold Accelerate Failure Time Model.'' \url{https://cran.r-project.org/web/packages/MTAFT/index.html}.
\end{etaremune}
\end{document}
