%-----------Conference Presentations-----------
\ifzh
  \section{学术报告与会议}
  \resumeSubHeadingListStart
      \resumeSubSubheading
          {{2021年全国数量经济学博士生学术论坛} \textbf{报告}}{2021年12月，厦门}
      \resumeSubSubheading
          {{2021年厦门大学现代统计学研讨会} \textbf{报告}}{2021年12月，厦门}
      \resumeSubSubheading
          {{NSFC计量建模与经济政策研究基础科学中心项目2023博士生年度论坛} \textbf{邀请报告}}{2023年11月，北京}
      \resumeSubSubheading
          {{全国工业统计学教学研究会青年统计学家协会 2024 年年会暨第二届中国青年统计学家论坛} \textbf{海报展示}}{2024年3月，徐州}
      \resumeSubSubheading
          {{首届国科大与厦大经济管理统计优秀博士毕业生论坛} \textbf{邀请报告}}{2024年6月，厦门}
      \resumeSubSubheading
          {{第二届全国统计与数据科学联合会议} \textbf{邀请报告}}{2024年7月，昆明}
      \resumeSubSubheading
          {{第十三届全国概率统计会议} \textbf{报告}}{2024年11月，厦门}
      \resumeSubSubheading
          {{第三届全国统计与数据科学联合会议} \textbf{海报展示}}{2025年7月，杭州}
      \resumeSubSubheading
          {{第42届国际机器学习大会(ICML)} \textbf{海报展示}}{2025年7月，加拿大温哥华}
      \resumeSubSubheading
          {{2025年厦门大学现代统计学研讨会} \textbf{报告}}{2025年12月，厦门}
  \resumeSubHeadingListEnd
\else
  \section{Conference Presentations}
  \resumeSubHeadingListStart
      \resumeSubSubheading
          {Talk in \textbf{The 2021 Forum for Doctoral Students in Quantitative Economics}}{Dec. 2021, Xiamen}
      \resumeSubSubheading
          {Talk in \textbf{Xiamen University 2021 Symposium on Modern Statistics}}{Dec. 2021, Xiamen}
      \resumeSubSubheading
          {Invited Talk in \textbf{2023 PhD Forum on Econometric Modeling and Economic Policy Research}}{Nov. 2023, Beijing}
      \resumeSubSubheading
          {Poster in \textbf{Conference of the Youth Association of the Chinese Association for Industrial Statistics}}{Mar. 2024, Xuzhou}
      \resumeSubSubheading
          {Invited Talk in \textbf{The 1st Outstanding PhD Forum in Economics and Management Statistics}}{Jun. 2024, Xiamen}
      \resumeSubSubheading
          {Invited Talk in \textbf{The 2nd Joint Conference on Statistics and Data Science}}{Jul. 2024, Kunming}
      \resumeSubSubheading
          {Talk in \textbf{The 13th Conference on Probability and Statistics}}{Nov. 2024, Xiamen}
      \resumeSubSubheading
          {Poster in \textbf{The 3rd Joint Conference on Statistics and Data Science}}{Jul. 2025, Hangzhou}
      \resumeSubSubheading
          {Poster in \textbf{Forty-Second International Conference on Machine Learning}}{Jul. 2025, Vancouver, Canada}     
      \resumeSubSubheading
          {Talk in \textbf{Xiamen University 2025 Symposium on Modern Statistics}}{Dec. 2025, Xiamen}
  \resumeSubHeadingListEnd
\fi
