%-----------PUBLICATIONS-----------
\section{Publications}
(* means corresponding author, $^\dagger$ means equal contribution, \(^\diamond\) means supervised students.)
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Journal Articles}}{}
\resumeItemListStart
  \resumeItem{\textbf{Hao Zeng}, Wei Zhong, \& Xingbai Xu (2025). ``Transfer Learning for Spatial Autoregressive Models with Application to U.S. Presidential Election Prediction.'' (Accepted for \textbf{Journal of Business \& Economic Statistics}, econometrics and statistics top journal)} 
  \resumeItem{Kangdao Liu, Tianhao Sun, \textbf{Hao Zeng}, Yongshan Zhang, Chi-Man Pun, \& Chi-Man Vong (2025). ``Spatial-Aware Conformal Prediction for Trustworthy Hyperspectral Image Classification.'' \textbf{IEEE Transactions on Circuits and Systems for Video Technology} 35 (9): 8754–8766. (CAS Q1 journal, Top)}
  \resumeItem{\textbf{Hao Zeng}, Chuang Wan, Wei Zhong, \& Tuo Liu (2024). ``Robust Integrative Analysis via Quantile Regression with Homogeneity and Sparsity.'' \textbf{Journal of Statistical Planning and Inference} 234 (January): 106196.}
  \resumeItem{Chuang Wan$^\dagger$, \textbf{Hao Zeng$^\dagger$*}, Wenyang Zhang$^\dagger$, Wei Zhong$^\dagger$, \& Changliang Zou$^\dagger$ (2024). ``Data‐driven Estimation for Multithreshold Accelerated Failure Time Model.'' \textbf{Scandinavian Journal of Statistics} 52 (1): 447–468.}
  \resumeItem{Wenqian Chen, \textbf{Hao Zeng}, Xiaoya Wang, Qiuping Xu, Panpan Liu, Liwei Zhang, Yingyue Hou, Qing Luo, Xueye Liu, Zhe Jiang, Zhiyuan Zhou, Jiang Chen, \& Jing Guo (2022). ``A Structural Equation Modeling Approach to Determine the Correlation between the Vertical and Sagittal Skeletal Patterns and Posterior Basal Bones Mismatching in Patients with Skeletal Class III Malocclusion.'' \textbf{American Journal of Orthodontics and Dentofacial Orthopedics} 162 (6): e277–294. (Cover paper)}
  \resumeItem{Wenqian Chen, \textbf{Hao Zeng}, Luna Sun, Qiuping Xu, Zhenxue Chen, Yunhan Sun, Qi Jia, Chengyun Liu, \& Jing Guo (2021). ``Match of the Bimaxillary Basal Bone Arches and Its Variations among Individuals.'' \textbf{Scanning} 2021 (1): 9625893.}
\resumeItemListEnd

  \resumeProjectHeading{\textbf{Conference Papers}}{}
  \resumeItemListStart
    \resumeItem{\textbf{Hao Zeng$^\dagger$}, Kangdao Liu$^\dagger$, Bingyi Jing, \& Hongxin Wei (2025). ``Parametric Scaling Law of Tuning Bias in Conformal Prediction.'' \textbf{42nd International Conference on Machine Learning (ICML 2025)}. (AI/ML Top)}
    \resumeItem{Huajun Xi$^\diamond$, Kangdao Liu, \textbf{Hao Zeng}, Wenguang Sun, \& Hongxin Wei (2025). ``Exploring the Noise Robustness of Online Conformal Prediction.'' \textbf{39th Annual Conference on Neural Information Processing Systems (NeurIPS 2026)}. (AI/ML Top)}
    \resumeItem{Kangdao Liu, \textbf{Hao Zeng}, Jianguo Huang, Huiping Zhuang, Chi-Man Vong, \& Hongxin Wei (2025). ``C-Adapter: Adapting Deep Classifiers for Efficient Conformal Prediction Sets.'' \textbf{28th European Conference on Artificial Intelligence}.}
  \resumeItemListEnd
    
    \resumeProjectHeading
      {\textbf{Working Papers}}{}
      \resumeItemListStart
        \resumeItem{Jingyi Zhang$^\diamond$, Yang Yue, Wei Zhong, \& \textbf{Hao Zeng*} (2025). ``Robust Estimation of Grouped Network Vector Autoregression: An Empirical Analysis Based on China Air Quality Data.'' (Submitted to \textbf{Statistical Research})}
        \resumeItem{Huipeng Huang$^\diamond$, Wenbo Liao, Huajun Xi, \textbf{Hao Zeng}, Mengchen Zhao, \& Hongxin Wei (2025). ``Selective Labeling with False Discovery Rate Control.'' (Submitted to \textbf{The 14th International Conference on Learning Representations (ICLR 2026)})}
        \resumeItem{Zhenlong Liu$^\diamond$, \textbf{Hao Zeng}, Weiran Huang, \& Hongxin Wei (2025). ``High-Power Training Data Identification with Provable Statistical Guarantees.'' (Submitted \textbf{to The 14th International Conference on Learning Representations (ICLR 2026)})}
        \resumeItem{\textbf{Hao Zeng}$^\dagger$, Jianguo Huang$^\dagger$\(^\diamond\), Bingyi Jing, Hongxin Wei, \& Bo An (2025). ``PAC Reasoning: Controlling the Performance Loss for Efficient Reasoning.'' (Submitted to Th\textbf{e 14th International Conference on Learning Representations (ICLR 2026)})}
        \resumeItem{Hongfu Gao, Feipeng Zhang, \textbf{Hao Zeng}, Deyu Meng, Bingyi Jing, \& Hongxin Wei (2025). ``Exploring Imbalanced Annotations for Effective In-Context Learning.'' (Submitted to\textbf{ The 14th International Conference on Learning Representations (ICLR 2026)})}
        \resumeItem{Xuanning Zhou$^\diamond$, Zihao Shi$^\diamond$, \textbf{Hao Zeng}, Xiaobo Xia, Bingyi Jing, \& Hongxin Wei (2025). ``Semi-Supervised Conformal Prediction with Unlabeled Nonconformity Score.'' (Submitted to \textbf{The IEEE/CVF Conference on Computer Vision and Pattern Recognition 2026 (CVPR 2026)})}
        \resumeItem{\textbf{Hao Zeng}, Bingyi Jing, \& Hongxin Wei (2025). ``Conditional Tuning in Conformal Prediction.''} 
        \resumeItem{\textbf{Hao Zeng}, Bingyi Jing, \& Hongxin Wei (2025). ``The Double Descent of Conformal Prediction.''} 
        \resumeItem{\textbf{Hao Zeng}, Kangdao Liu, Bingyi Jing, \& Hongxin Wei (2025). ``On Tuning Bias in Conformal Prediction.''} 
        \resumeItem{\textbf{Hao Zeng}, \& Jianguo Huang$^\diamond$ (2025). ``PAC Accelerate: A Statistically Guaranteed Acceleration Method for Large Generative Models.''}
        \resumeItem{\textbf{Hao Zeng}, \& Jianguo Huang$^\diamond$ (2025). ``Group-Conditional PAC Reasoning: Groupwise Efficient Reasoning with Statistical Guarantees.''}
        \resumeItem{\textbf{Hao Zeng} (2025). ``A Note on the Impossibility of Conditional PAC-Efficient Reasoning.''}
        \resumeItem{\textbf{Hao Zeng}, Jiajun Sun$^\diamond$, Bingyi Jing, \& Wei Zhong (2025). ``Test-time Valid Selection of Conformal Sets via Gaussian Stability.''}
        \resumeItem{\textbf{Hao Zeng}, Junxian Liu$^\diamond$, Bingyi Jing, \& Hongxin Wei (2025). ``Efficient Backward Conformal Prediction.''}
        \resumeItem{\textbf{Hao Zeng}, Wei Zhong, Chuang Wan (2025). ``Selective Inference for the Identified Groups in Network Vector Autoregressive Model.''}
        \resumeItem{\textbf{Hao Zeng}, Huipeng Huang, Jianguo Huang, Bingyi Jing, \& Hongxin Wei (2025). ``HyPAC: Hybrid Labeling for LLMs via Multi-level PAC Reasoning.''}
      \resumeItemListEnd
    
    \resumeProjectHeading
      {\textbf{Software}}{}
      \resumeItemListStart
        \resumeItem{Chuang Wan, \textbf{Hao Zeng}, Wei Zhong, \& Changliang Zou (2023). ``MTAFT: Data-Driven Estimation for Multi-Threshold Accelerate Failure Time Model.'' \href{https://cran.r-project.org/web/packages/MTAFT/index.html}{https://cran.r-project.org/web/packages/MTAFT/index.html}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
